The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-11 rational.tex
_

Let us use the shorthand {{b1 -o+ b2 = 0 <-> -b1 + b2}}. See
Sec. \ref{sec:hof} for a discussion of the additive functions
vs. multiplicative functions.

@@

While the constructions in Sec \ref{sec:monoidal-constructions} apply
to both the {{(0,+)}} and {{(1,*)}} monoids, each construction
presented here applies to a specific monoid.

>>>>

Let us use the shorthand {{b1 -o+ b2 = 0 <-> -b1 + b2}}. See
Sec. \ref{sec:hof} for a discussion of the additive functions
vs. multiplicative functions. \roshan{Where is the HOF discussion?}

@@

While the constructions in Sec \ref{sec:neg} apply to both the
{{(0,+)}} and {{(1,*)}} monoids, each construction presented here
applies to a specific monoid.

\roshan{Each of these isomorphisms has baffled us -- either we
  believed they were not constructible. Or we have struggled to
  comprehend what they mean. Hence it is worth saying a sentence or
  two about each beyond how they are constructed.}
